---
title: "BAMA_PrimaryQC_Script_v2-SA"
author: "Sergey Ananyev"
date: "2024-07-31"
output: html_document
---

``````{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())


if(!require(tidyverse)){
    install.packages("tidyverse",dependencies = T)
    library(tidyverse)
  }
if(!require(ggplot2)){
    install.packages("ggplot2",dependencies = T)
    library(ggplot2)
  }
if(!require(MESS)){
    install.packages("MESS",dependencies = T)
    library(MESS)
  }
if(!require(gridExtra)){
    install.packages("gridExtra",dependencies = T)
    library(gridExtra)
  }
if(!require(grid)){
    install.packages("grid",dependencies = T)
    library(grid)
  }
if(!require(ggsignif)){
    install.packages("ggsignif",dependencies = T)
    library(ggsignif)
  }
if(!require(data.table)){
    install.packages("data.table",dependencies = T)
    library(data.table)
  }
if(!require(dplyr)){
    install.packages("dplyr",dependencies = T)
    library(dplyr)
  }
if(!require(ggplate)){
    install.packages("ggplate",dependencies = T)
    library(ggplate)
  }
if(!require(readxl)){
    install.packages("readxl",dependencies = T)
    library(readxl)
  }
if(!require(pzfx)){
    install.packages("pzfx",dependencies = T)
    library(pzfx)
  }
if(!require(readr)){
    install.packages("readr",dependencies = T)
    library(readr)
  }
if(!require(naniar)){
    install.packages("naniar",dependencies = T)
    library(naniar)
  }
if(!require(rlist)){
    install.packages("rlist",dependencies = T)
    library(rlist)
  }
if(!require(drc)){
    install.packages("drc",dependencies = T)
    library(drc)
  }
if(!require(stats)){
    install.packages("stats",dependencies = T)
    library(stats)
  }
if(!require(tibble)){
    install.packages("tibble",dependencies = T)
    library(tibble)
  }
if(!require(fuzzyjoin)){
    install.packages("fuzzyjoin",dependencies = T)
    library(fuzzyjoin)
  }
```

# Data Entry

```{r}

rawDataFolder <- "Z:/Data/Adelaide Fuller/CMV/BAMA/3_raw/CMV004_formal/IgG/"

workingDirectory <- "Z:/Data/Adelaide Fuller/CMV/BAMA/"

standardCurve <- "Cytogam"

cvCutoff <- 25

blankBeadCutoff <- 1000

lowbeadcountcutoff <- 100

lowMFI <- 100

headerrows <- 7

dilutionfactor <- 250

sampledilutionpath <- NA

dilutioncurvepath <- NA


```

# Import Data

```{r}
# Define the function to read multiple sheets from an Excel file
multipleSheetReader <- function(fname) {
  # Get info about all excel sheets
  sheets <- readxl::excel_sheets(fname)
  tibble <- lapply(sheets, function(x) readxl::read_excel(fname, sheet = x))
  data_frame <- lapply(tibble, as.data.frame)
  
  # Assigning names to data frames
  names(data_frame) <- sheets
  
  # Return data frame
  return(data_frame)
}

# Define the function to process all files in a directory
processAllFiles <- function(rawDataFolder) {
  # Get all file names in the directory
  fileNames <- list.files(rawDataFolder, full.names = TRUE)
  
  # Apply the multipleSheetReader function to all files
  allData <- lapply(fileNames, multipleSheetReader)
  
  # Assigning names to the list elements
  names(allData) <- basename(fileNames)
  
  return(allData)
}

# Call the function
allData <- processAllFiles(rawDataFolder)
```

# Sampling error check

```{r}
# Define the function to process the data
processSamplingErrorsData <- function(rawData, headerrows, dilutioncurvepath) {
  # Import blanks dataframe as new dataframe
  if (!is.na(dilutioncurvepath)) {
    dilutionCurves <- read.csv(dilutioncurvepath)
  }
  
  # Check for sampling errors and create list of bead names
  sampleRowRaw <- as.data.frame(rawData$`Sampling Errors`)
  
  # Insert a sample description column if there isn't one
  sampleDescIndex <- as.list(which(apply(sampleRowRaw, 2, function(x) any(grepl("description", x, ignore.case = TRUE)))))
  if (length(sampleDescIndex) == 0) {
    sampleRowRaw <- add_column(sampleRowRaw, x = "none", .after =2)
  }
  
  # Change the column names for working on the data
  colnames(sampleRowRaw) <- c(letters[1:ncol(sampleRowRaw)])
  
  # Remove unnecessary rows
  sampleRowRaw <- sampleRowRaw[headerrows:nrow(sampleRowRaw), ]
  
  # Generate list of the bead names on the panel
  beadNames <- as.list(sampleRowRaw[1,])
  beadNames <- beadNames[-c(1:3)]
  
  # Select only the rows we want to keep
  sampleRowRaw <- filter(sampleRowRaw, !grepl('Type', a))
  sampleRowRaw <- filter(sampleRowRaw, !grepl('Sampling Errors: 1 - Low bead #', a))
  sampleRowRaw <- filter(sampleRowRaw, !grepl('= Value not available', a))
  sampleRowRaw <- filter(sampleRowRaw, !grepl('OOR = Out of Range', a))
  sampleRowRaw <- filter(sampleRowRaw, !grepl('Exp Conc = Expected Concentration', a))
  
  # Check for sample errors and filter if error present
  sampleErrorQC <- sampleRowRaw %>%
    filter(if_all(-c(a, b, c), ~ !is.na(.)), if_any(c(a), ~ !is.na(.)))
  
  # Update colnames
  colnames(sampleErrorQC) <- c("sample type", "well", "sample description", paste(beadNames))
  if (nrow(sampleErrorQC) == 0){
    sampleErrorQC[1,1] <- c("No sampling errors")
  }
  
  # Convert all to character
  sampleErrorQC <- mutate_all(sampleErrorQC, function(x) (as.character(x)))
  
  # Add id column
  sampleErrorQC <- cbind(id = "Sample Errors", sampleErrorQC)
  
  return(sampleErrorQC)
}

# Apply the function to all data
allData.SamplingErrorsProcessed <- lapply(allData, function(x) processSamplingErrorsData(x, headerrows, dilutioncurvepath))

```


# Check for low bead count

```{r}

# Define the function to process the data
processData <- function(rawData, headerrows, lowbeadcountcutoff) {
  # Set dataframe
  beadCountRaw <- as.data.frame(rawData$`Bead Count`)
  
  # Insert a sample description if there isn't one
  beadCountDescIndex <- as.list(which(apply(beadCountRaw, 2, function(x) any(grepl("description", x, ignore.case = TRUE)))))
  if (length(beadCountDescIndex) == 0) {
    beadCountRaw <- add_column(beadCountRaw, x = "none", .after = 2)
  }
  
  # Update colnames
  colnames(beadCountRaw) <- c(letters[1:ncol(beadCountRaw)])
  
  # Remove unnecessary rows
  beadCountRaw <- beadCountRaw[headerrows:nrow(beadCountRaw), ]
  
  # Generate list of the bead names on the panel
  beadNames <- as.list(beadCountRaw[1,])
  beadNames <- beadNames[-c(1:3)]
  
  # Select only the rows we want to keep
  beadCountRaw <- filter(beadCountRaw, !grepl('Type', a))
  beadCountRaw <- filter(beadCountRaw, !grepl('Sampling Errors: 1 - Low bead #', a))
  beadCountRaw <- filter(beadCountRaw, !grepl('= Value not available', a))
  beadCountRaw <- filter(beadCountRaw, !grepl('Value = Value extrapolated', a))
  beadCountRaw <- filter(beadCountRaw, !grepl('OOR = Out of Range', a))
  beadCountRaw <- filter(beadCountRaw, !grepl('Exp Conc = Expected Concentration', a))
  
  # Make sure the columns are numeric
  if (ncol(beadCountRaw) == 4) {
    beadCountRaw[4] <- as.data.frame(as.numeric(beadCountRaw[,4]))
  } else {
    beadCountRaw[4:ncol(beadCountRaw)] <- sapply(beadCountRaw[4:ncol(beadCountRaw)], function(x) as.numeric(x))
  }
  
  # Check for low bead counts and filter if error is present
  beadCountQC <- beadCountRaw %>%
    filter(if_any(-c(a, b, c), ~ !is.na(.)), if_any(-c(a, b, c), ~ . < lowbeadcountcutoff), if_all(c(a), ~ !is.na(.)))
  
  # Rename columns
  colnames(beadCountQC) <- c("sample type", "well", "sample description", paste(beadNames))
  
  # Update the error dataframe
  if (nrow(beadCountQC) == 0) {
    beadCountQC[1,1] <- c("No low beadcounts")
  }
  beadCountQC <- mutate_all(beadCountQC, function(x) (as.character(x)))
  
  # Add id column
  beadCountQC <- cbind(id = "Low Bead Counts", beadCountQC)
  
  return(beadCountQC)
}

# Apply the function to all data
allData.BeadCountProcessed <- lapply(allData, function(x) processData(x, headerrows, lowbeadcountcutoff))


```

# Check for high CV

```{r}
# Define the function to process the data
processCVData <- function(rawData, headerrows, cvCutoff) {
  # Set dataframe
  highCVRaw <- as.data.frame(rawData$`%CV`)
  
  # Insert a sample description if there isn't one
  highCVDescIndex <- as.list(which(apply(highCVRaw, 2, function(x) any(grepl("description", x, ignore.case = TRUE)))))
  if (length(highCVDescIndex) == 0) {
    highCVRaw <- add_column(highCVRaw, x = "none", .after = 2)
  }
  
  # Update column names
  colnames(highCVRaw) <- c(letters[1:ncol(highCVRaw)])
  
  # Remove unnecessary rows
  highCVRaw <- highCVRaw[headerrows:nrow(highCVRaw), ]
  
  # Generate list of the bead names on the panel
  beadNames <- as.list(highCVRaw[1,])
  beadNames <- beadNames[-c(1:3)]
  
  # Select only the rows we want to keep
  highCVRaw <- filter(highCVRaw, !grepl('Type', a))
  highCVRaw <- filter(highCVRaw, !grepl('Sampling Errors: 1 - Low bead #', a))
  highCVRaw <- filter(highCVRaw, !grepl('= Value not available', a))
  highCVRaw <- filter(highCVRaw, !grepl('Value = Value extrapolated', a))
  highCVRaw <- filter(highCVRaw, !grepl('OOR = Out of Range', a))
  highCVRaw <- filter(highCVRaw, !grepl('Exp Conc = Expected Concentration', a))
  
  # Make sure the columns are numeric
  if (ncol(highCVRaw) == 4) {
    highCVRaw[4] <- as.data.frame(as.numeric(highCVRaw[,4]))
  } else {
    highCVRaw[4:ncol(highCVRaw)] <- sapply(highCVRaw[4:ncol(highCVRaw)], function(x) as.numeric(x))
  }
  
  # Check for low high CVs and filter if error is present
  highCVqc <- highCVRaw %>%
    filter(if_any(-c(a, b, c), ~ !is.na(.)), if_any(-c(a,b,c), ~ . >= cvCutoff), if_all(c(a), ~ !is.na(.)))
  
  # Rename columns
  colnames(highCVqc) <- c("sample type", "well", "sample description", paste(beadNames))
  
  # Update the error dataframe
  if (nrow(highCVqc) == 0) {
    highCVqc[1,1] <- c("No high %CVs")
  }
  highCVqc <- mutate_all(highCVqc, function(x) (as.character(x)))
  
  # Add new column
  highCVqc <- cbind(id = "High %CVs", highCVqc)
  
  return(highCVqc)
}

# Apply the function to all data
allData.CVProcessed <- lapply(allData, function(x) processCVData(x, headerrows, cvCutoff))

```

# Check blank well

```{r}
# Define the function to process the data
processBlankWellData <- function(rawData) {

  # Set dataframe
  blanks <- as.data.frame(rawData$`FI - Bkgd`)
  
  # Insert a sample description column if there isn't one
  blankDescIndex <- as.list(which(apply(blanks, 2, function(x) any(grepl("description", x, ignore.case = TRUE)))))
  if (length(blankDescIndex) == 0) {
    blanks <- add_column(blanks, x = "none", .after = 2)
  }
  
  # Update colnames
  colnames(blanks) <- c(letters[1:ncol(blanks)])
  
  # Pull out the blank well rows
  blankWellValues <- blanks %>%
    filter(a == "B")
  blankWellValues <- blankWellValues[4:ncol(blankWellValues)]
  blankWellValues <- mutate_all(blankWellValues, function(x) as.numeric(as.character(x)))
  
  # Identify the min and max
  blankWellMin <- min(blankWellValues)
  blankWellMax <- max(blankWellValues)
  
  # Create QC dataframe
  blankWellCriteria <- c("blank well min", "blank well max")
  blankWellValuesQC <- c(blankWellMin, blankWellMax)
  blankWellQC <- data.frame(blankWellCriteria, blankWellValuesQC)
  colnames(blankWellQC) <- c("sample type", "well")
  
  # Update the error dataframe
  if (nrow(blankWellQC) == 0) {
    blankWellQC[1,1] <- c("No high %CVs")
  }
  blankWellQC <- mutate_all(blankWellQC, function(x) as.character(x))
  
  # Add new column
  blankWellQC <- cbind(id = "Blank Well MFIs Min/Max", blankWellQC)
  
  return(blankWellQC)
}

# Apply the function to all data
allData.BlankWellProcessed <- lapply(allData, processBlankWellData)

```

# Check for blank bead MFI

```{r}
# Define the function to process the data
processBlankBeadData <- function(rawData, headerrows, blankBeadCutoff) {
  # Set dataframe
  blankBeadRaw <- as.data.frame(rawData$`FI - Bkgd`)
  
  # Insert a sample description column if there isn't one
  blankDescIndex <- as.list(which(apply(blankBeadRaw, 2, function(x) any(grepl("description", x, ignore.case = TRUE)))))
  if (length(blankDescIndex) == 0) {
    blankBeadRaw <- add_column(blankBeadRaw, x = "none", .after = 2)
  }
  
  # Update colnames
  colnames(blankBeadRaw) <- c(letters[1:ncol(blankBeadRaw)])
  
  # Remove unnecessary rows
  blankBeadRaw <- blankBeadRaw[headerrows:nrow(blankBeadRaw), ]
  
  # Generate list of the bead names on the panel
  beadNames <- as.list(blankBeadRaw[1,])
  beadNames <- beadNames[-c(1:3)]
  
  # Select only the rows we want to keep
  blankBeadRaw <- filter(blankBeadRaw, !grepl('Type', a))
  blankBeadRaw <- filter(blankBeadRaw, !grepl('Sampling Errors: 1 - Low bead #', a))
  blankBeadRaw <- filter(blankBeadRaw, !grepl('= Value not available', a))
  blankBeadRaw <- filter(blankBeadRaw, !grepl('Value = Value extrapolated', a))
  blankBeadRaw <- filter(blankBeadRaw, !grepl('OOR = Out of Range', a))
  blankBeadRaw <- filter(blankBeadRaw, !grepl('Exp Conc = Expected Concentration', a))
  
  # Identify which column has the blank bead
  index <- as.numeric(which(apply(blankBeadRaw, 2, function(x) any(grepl("blank", x, ignore.case = TRUE)))))
  if (as.numeric(length(index)) > 1) {
    index <- index[-1]
  }
  
  # Check to see if a blank bead was detected and return error if not detected
  # Proceed with checking blank bead MFI if blank bead IS detected
  if (length(index) == 0) {
    blankBeadQC <- setNames(data.frame(matrix(ncol = (13 + length(beadNames)), nrow = 0)), c("sample type", "well", "sample description", paste(beadNames)))
    blankBeadQC[1,1] <- as.data.frame("ERROR: No blank bead detected")
  } else {
    # Make sure the columns are numeric
    if(ncol(blankBeadRaw) == 4) {
      blankBeadRaw[4] <- as.data.frame(as.numeric(blankBeadRaw[,4]))
    } else {
      blankBeadRaw[4:ncol(blankBeadRaw)] <- sapply(blankBeadRaw[4:ncol(blankBeadRaw)], function(x) as.numeric(x))
    }
    
    # Pull out values from this column that are higher than blank bead cutoff
    blankBeadQC <- blankBeadRaw %>%
      filter(blankBeadRaw[index] > blankBeadCutoff)
    
    # Rename columns
    colnames(blankBeadQC) <- c("sample type", "well", "sample description", paste(beadNames))
    
    # Update the error dataframe
    if (nrow(blankBeadQC) == 0) {
      blankBeadQC[1,1] <- as.data.frame("No high blank bead wells")
    }
    blankBeadQC <- mutate_all(blankBeadQC, function(x) as.character(x))
    
    # Add id column
    blankBeadQC <- cbind(id = "Blank Bead MFIs", blankBeadQC)
  }
  
  return(blankBeadQC)
}

# Apply the function to all data
allData.BlankBeadProcessed <- lapply(allData, function(x) processBlankBeadData(x, headerrows, blankBeadCutoff))

```
# Prep Data for interpolation and export to prism

```{r}
interpolateAndProcessData <- function(rawData, assayName, headerrows, blankBeadCutoff, standardCurve, dilutionfactor, workingDirectory, dilutioncurvepath, sampledilutionpath, allData, SamplingErrorsProcessed, BeadCountProcessed, CVProcessed, BlankWellProcessed, BlankBeadProcessed, currentIteration, cvCutoff, lowbeadcountcutoff, lowMFI){


   # Trim "_RAW.xlsx" from the end of assayName
  assayName <- sub("_RAW\\.xlsx$", "", assayName)
  
  # Define the file paths using the assayName
  qcpath <- paste(workingDirectory, "5_qc/CMV004_formal/IgG/", assayName, "_QC.csv", sep = "")
  prismpath <- paste(workingDirectory,"6_prism_figures/CMV004_formal/", assayName,"_PRISM.pzfx", sep = "")
  mfirawpath <- paste(workingDirectory, "4_analyzed/CMV004_formal/FILTERED_MFIs/IgG/", assayName, "_MFIs.csv", sep = "")
  noninterpolatedpath <- paste(workingDirectory, "4_analyzed/CMV004_formal/OUTLIERS/IgG/", assayName, "_OUTLIERS.csv", sep = "")
  interpolatedconcpath <- paste(workingDirectory, "4_analyzed/CMV004_formal/INTERPLTDL_CONC/IgG/", assayName, "_INTERPLTDL_CONC.csv", sep = "")
  mfirawpath_unfiltered <- paste(workingDirectory, "4_analyzed/CMV004_formal/RAW_MFIs/IgG/", assayName, "_MFIs-unfiltered.csv", sep = "")
  interpolated_filtered <- paste(workingDirectory, "4_analyzed/CMV004_formal/FILTERED_INTERPLTDL/IgG/", assayName, "_INTERPLTDL_CONC-filtered.csv", sep = "")   
  
  # Set dataframe

mfisRaw <- as.data.frame(rawData$`FI - Bkgd`)

# Insert a sample description column if there isn't one

mfiDescIndex <- as.list(which(apply(mfisRaw, 2, function(x) any(grepl("description", x, ignore.case = TRUE)))))
if (length(mfiDescIndex) == 0) {
  mfisRaw <- add_column(mfisRaw, x = "none", .after = 2)
}

# Update column names

colnames(mfisRaw) <- c(letters[1:ncol(mfisRaw)])

# Remove unnecessary rows 

mfisRaw <- mfisRaw[headerrows:nrow(mfisRaw), ]

# select only the rows we want to keep

mfisRaw <- filter(mfisRaw, !grepl('Type', a))
mfisRaw <- filter(mfisRaw, !grepl('Sampling Errors: 1 - Low bead #', a))
mfisRaw <- filter(mfisRaw, !grepl('= Value not available', a))
mfisRaw <- filter(mfisRaw, !grepl('Value = Value extrapolated', a))
mfisRaw <- filter(mfisRaw, !grepl('OOR = Out of Range', a))
mfisRaw <- filter(mfisRaw, !grepl('Exp Conc = Expected Concentration', a))

# Take out the well

mfisRaw$b <- NULL

# Generate list of the bead names on the panel
  beadNames <- as.list(mfisRaw[1,])
  beadNames <- beadNames[-c(1:2)]

# Update column names

mfisRaw <- mfisRaw[-1,]
colnames(mfisRaw) <- c("sampletype", "sampledescription", paste(beadNames))

# Only keep the number of rows as there are unique samples (in order to remove the individual data points)

sampleNumber <- as.numeric(length(unique(na.omit(mfisRaw$sampletype))))
mfisRaw <- mfisRaw[1:sampleNumber, ]

# if the sample type is "B" put blank in the description column

mfisRaw$sampledescription <- ifelse(mfisRaw$sampletype == "B", "blank", mfisRaw$sampledescription)

# remove the sampletype column

mfisRaw$sampletype <- NULL

# Make sure the bead columns are numeric

if (ncol(mfisRaw)==2) {
  mfisRaw[2] <- as.data.frame(as.numeric(mfisRaw[,2]))
} else {
  mfisRaw[2:ncol(mfisRaw)] <- sapply(mfisRaw[2:ncol(mfisRaw)], function(x) as.numeric(x))
}

# Split by standard curve value and others
# Create a simple plot (you can customize this further)
plot(1, type = "n", xlim = c(0, 1), ylim = c(0, 1), xlab = "", ylab = "")
mfiSTD <- mfisRaw %>%
  filter(grepl(paste0("^", standardCurve), sampledescription, ignore.case = TRUE))
mfiSTDpzfx <- mfiSTD[,-1]
mfiSTDpzfx <- as.matrix(mfiSTDpzfx)
rownames(mfiSTDpzfx) <- mfiSTD[,1]

mfiSamples <- mfisRaw %>%
  filter(!grepl(standardCurve, sampledescription, ignore.case = TRUE))
mfiSamplespzfx <- mfiSamples[,-1]
mfiSamplespzfx <- as.matrix(mfiSamplespzfx)
rownames(mfiSamplespzfx) <- mfiSamples[,1]

## Interpolation of standard curves
# create color palette

if (length(beadNames<20)){colpalette <- c("#f44336", "#ff9800","#ffeb3b","#4caf50","#03a9f4","#9c27b0","#795548", 
                                          "#e81e63","#ffc107","#cddc39","#00bcd4","#3f51b5","#9e9e9e",
                                          "#ff5722","#8bc34a", "#2196f3", "#673ab7", "#009688","#000000","#607d8b")
} else {
  colpalette <- rainbow(50)
}

# Check if there's a standard curve
# If yes, proceed with interpolation
# If not, write out raw MFIs

if (nrow(mfiSTD) == 0) {
  write.csv(mfiSamples, mfirawpath, row.names = FALSE)
} else {
  
  # create empty vectors
  
  sampleConcentrations <- as.data.frame(mfiSamples$sampledescription)
  insideCurve <- as.data.frame(mfiSamples$sampledescription)
  outsideCurve <- as.data.frame(mfiSamples$sampledescription)
  sample.dil.x.conc <- as.data.frame(mfiSamples$sampledescription)
  stdcurveplot <- setNames(data.frame(matrix(ncol =1, nrow = 0)), c("m.fit"))
  
  # Edit the cytogam data
  # Add column for concentration to the cytogam datasheet
  
  mfiSTD <- add_column(mfiSTD, dilution = NA)
  
  # Extract numbers from the description column
  
  mfiSTD$dilution <- as.numeric(parse_number(mfiSTD$sampledescription))
  
    if (!is.na(dilutioncurvepath)){
      dilutioncolnames <- as.list(colnames(dilutioncurves[2:ncol(dilutioncurves)]))
      mfiSTDtemp <- mfiSTD[unlist(lapply(gsub("^[A-Za-z]?", "", dilutioncolnames), function(x) grep(x, names(mfiSTD))))] #take out columns not in the imported standard curve file
      mfiSTDtemp <- mfiSTDtemp[!duplicated(as.list(mfiSTDtemp))]
      mfiSTDdils <- mfiSTD[!mfiSTD %in% mfiSTDtemp]
      for (i in (2:(ncol(mfiSTDdils)-1))){
        mfiSTDdils[,i] <- mfiSTDdils$dilution
      }
      # rename dilution curve columns
      temp.dil <- data.frame(dilution = paste(dilutioncolnames))
      temp.beads <- data.frame(beads = paste(beadNames))                                        
      temp <- fuzzy_left_join(temp.dil, temp.beads, by = c("dilution" = "beads"), match_fun = \(x,y) str_detect(y, x))
      temp <- as.list(unique(temp[,2]))
      colnames(dilutioncurves) <- c("dilution", paste(temp))
      mfiSTDdils <- full_join(mfiSTDdils, dilutioncurves, by = "dilution")
      col.order <- c("sampledescription", paste(beadNames), "dilution")
      mfiSTDdils <- mfiSTDdils[ , col.order]
      mfiSTDdils <- mfiSTDdils %>%
        drop_na(sampledescription)
      mfiSTDdils$dilution <- NULL
    }
    
    # create mfistddils if doesnt already exits
    if (!exists("mfiSTDdils")){
      mfiSTDdils <- as.data.frame(mfiSTD$sampledescription)
      for (i in (2:(ncol(mfiSTD)-1))){
        mfiSTDdils[,i] <- mfiSTD$dilution
      }
      colnames(mfiSTDdils) <- c("sampledescription", paste(beadNames))
    }
    
    # Modify the beadname vector
    for (i in (2:(ncol(mfiSTD) -1))) {
      # Generate a standard curve for each bead using log transformation
      createSTDcurve <- function(df, conc, mfi) {
        curves <- drm(mfi~conc, data = df, fct = LL.4(names = c("n", "Amin", "Amax", "EC50")))
      }
      stdCurve <- createSTDcurve(mfiSTD, mfiSTDdils[,i], mfiSTD[,i])
      
      
      if (exists("stdCurveplot")){
        stdCurveplot <- plot(stdCurve,
                             add = TRUE, 
                             type = "all", 
                             col = colpalette[i],
                             xlim = c(min(mfiSTDdils[2:ncol(mfiSTDdils)]), max(mfiSTDdils[2:ncol(mfiSTDdils)])),
                             ylim = c(0,30000),
                             pch =i, 
                             xlab = "concentration (ug/ml)", 
                             ylab = "MFI", 
                             legend = TRUE,
                             legendText = beadNames[i-1],
                             legendPos = c(10, (44000-((i-1)*2000))))
      } else {stdCurveplot <- plot(stdCurve, 
                                   type = "all", 
                                   col = colpalette[i], 
                                   xlim = c(min(mfiSTDdils[2:ncol(mfiSTDdils)]), max(mfiSTDdils[2:ncol(mfiSTDdils)])),
                                   ylim = c(0,30000),
                                   pch = i, 
                                   xlab = "concentration (ug/ml)", 
                                   ylab = "MFI", 
                                   legend = TRUE,
                                   legendText = beadNames[i-1],
                                   legendPos = c(10, (44000-((i-1)*2000))))
      }
      # https://carpentries-incubator.github.io/life-sciences-workshop/13-r-beyond-base-r/index.html
      
      Amin.est <- stdCurve[["coefficients"]][["Amin:(Intercept)"]]
      Amax.est <- stdCurve[["coefficients"]][["Amax:(Intercept)"]]
      EC50.est <- stdCurve[["coefficients"]][["EC50:(Intercept)"]]
      n.est <- stdCurve[["coefficients"]][["n:(Intercept)"]]
      
      ## interpolate all of the sample values
      
      ## check to see if the data falls within the linear range of the curve
      
      # min max of std curve
      linrangemax <- as.numeric(stdCurve[["coefficients"]][["Amax:(Intercept)"]])
      linrangemin <- as.numeric(stdCurve[["coefficients"]][["Amin:(Intercept)"]])
      
      # create a new dataframe that has all of the data points that are outside the linear range
      outsidecurve_add <- replace(mfiSamples[,i], (linrangemin < mfiSamples[,i]) & (mfiSamples[,i] < linrangemax), NA)
      outsideCurve <- cbind(outsideCurve, outsidecurve_add)
      
      # create a new data frame that has all of the data points that are inside the linear range
      insidecurve_add <- replace(mfiSamples[,i], (linrangemin > mfiSamples[,i]) | (mfiSamples[,i] > linrangemax), NA)
      insideCurve <- cbind(insideCurve, insidecurve_add) # bind sample names
      
      # interpolate the values within the linear range
      model <- as.data.frame(ED(stdCurve, insideCurve[,i], bound = FALSE, ci = "delta", type = "absolute"), row.names = FALSE)
      
      # add to the sample name outputs 
      sampleConcentrations <- bind_cols(sampleConcentrations, model, .name_repair = c("unique"))
    }
    
  # Change column headings
  beadNames2 <- rep(beadNames, each = 2)
  sampleConcColNames <- as.list(colnames(sampleConcentrations[2:ncol(sampleConcentrations)]))
  sampleConcentrationColNames <- as.list(c("sample.description"))
  for (i in 1:length(beadNames2)) {
    tempName <- paste(beadNames2[i], sampleConcColNames[i])
    sampleConcentrationColNames <- append(sampleConcentrationColNames, tempName)
  }
  colnames(sampleConcentrations)  <- c(sampleConcentrationColNames)
  
  ## multiply the samples by the dilution factor
  if (!is.na(dilutionfactor)){
    sampleconcdil <- (sampleConcentrations[2:ncol(sampleConcentrations)])
    sampleconcdil.est <-  sampleconcdil[, seq(1, ncol(sampleconcdil), by = 2)]
    sampleconcdil.est <- sampleconcdil.est*dilutionfactor
    sampleconcdil.err <-  sampleconcdil[, seq(2, ncol(sampleconcdil), by = 2)]
    sampleconcdil <- cbind(sampleconcdil.est, sampleconcdil.err)
    sample.dil.x.conc <- cbind(sample.dil.x.conc, sampleconcdil)
  } else if (!is.na(sampledilutionpath)){
    dilutionlist <- read.csv(sampledilutionpath)
    dilutionlist <- full_join(dilutionlist, sampleconcentrations, by = c("sample"="sample.description"))
    for (i in 3:(length(beadNames)+2)){
      multipliedcol <- dilutionlist$dilution*dilutionlist[,i]
      sample.dil.x.conc <- cbind(sample.dil.x.conc, multipliedcol)
    }
  } else {
    sample.dil.x.conc$output <- "No diltuion factor detected"
  }
  
  # Initialize QC_Frame_Set as a list of lists
  QC_Frame_Set <- list()
  
  # Loop over each data frame in the allDataProcessed list
  for(i in seq_along(allData)) {
    # Get the name of the current sublist
    assayName <- names(allData)[i]
    
    # Set mfisRaw as the `FI - Bkgd` data frame from the current list
    mfisRaw2 <- as.data.frame(allData[[i]]$`FI - Bkgd`)
    
    # Remove unnecessary rows
    mfisRaw2 <- mfisRaw2[7:nrow(mfisRaw2), ]
    
    # Generate list of the bead names on the panel
    beadNames <- as.list(mfisRaw2[1,])
    beadNames <- beadNames[-c(1:3)]
    
    # Add STDqc 
    if (is.na(standardCurve)){
      STDqc <- setNames(data.frame(matrix(ncol = 8, nrow = 0)), c("sample type", "well", "sample description", paste(beadNames)))
      STDqc[1,1] <- as.data.frame("No STD curve sample provided")
    } else if(!is.na(standardCurve) & nrow(mfisRaw)==0){
      STDqc <- setNames(data.frame(matrix(ncol = 8, nrow = 0)), c("sample type", "well", "sample description", paste(beadNames)))
      STDqc[1,1] <- as.data.frame("ERROR: No STD curve sample detected")
    } else {
      STDqc <- setNames(data.frame(matrix(ncol = (3+length(beadNames)), nrow = 0)), c("sample type", "well", "sample description", paste(beadNames)))
      STDqc[1,1] <- as.data.frame(standardCurve)
    }
    
    # Add new column
    STDqc <- cbind(id = "Standard Curve", STDqc)
    
    QC_Frame_Set[[assayName]] <- c(SamplingErrorsProcessed[i], BeadCountProcessed[i], CVProcessed[i], BlankBeadProcessed[i], BlankWellProcessed[i], list(STDqc))
  }
  
  # Now let's bind_rows each sublist within QC_Frame_Set
  for(i in seq_along(QC_Frame_Set)) {
  
    # Use bind_rows to combine all data frames in the sublist
    combined_df <- dplyr::bind_rows(QC_Frame_Set[[i]])

    # Replace the sublist in QC_Frame_Set with the combined data frame
    QC_Frame_Set[[i]] <- combined_df
  }
  

  # Get QC_filter_values from column 4 of the data frame within the QC_Frame_Set
  QC_filter_values <- QC_Frame_Set[currentIteration][[1]][,4]
  
  QC_File <- QC_Frame_Set[[currentIteration]]
  
  currentIteration <<- currentIteration + 1
  # write out values that were not plotted
  write.csv(outsideCurve, noninterpolatedpath, row.names = FALSE)
  
  # write out the raw MFIs and the interpolated sample concentrations
  write.csv(mfisRaw, mfirawpath_unfiltered, row.names = FALSE)
  write.csv(sample.dil.x.conc, interpolatedconcpath, row.names = FALSE)
  
  # Find the column that begins with "Blank"
  blank_col <- grep("^Blank", colnames(mfisRaw), value = TRUE)

  # Set values higher than blankbeadcutoff to NA in the "Blank" column
  mfisRaw[mfisRaw[[blank_col]] > blankBeadCutoff, blank_col] <- NA

  # Set values lower than lowMFI to NA in every column except the first one
  mfisRaw[, -1] <- lapply(mfisRaw[, -1], function(x) ifelse(x < lowMFI, NA, x))

  # The filtered data
  mfisFiltered <- mfisRaw
  
  # Filter out rows from sample.dil.x.conc where column 1 matches QC_filter_values
  interpolatedFiltered <- sample.dil.x.conc[!sample.dil.x.conc[,1] %in% QC_filter_values,]
  
  # Write out the filtered MFIs and the filtered interpolated sample concentrations
  write.csv(mfisFiltered, mfirawpath, row.names = FALSE)
  write.csv(interpolatedFiltered, interpolated_filtered, row.names = FALSE)
  write.csv(QC_File, qcpath, row.names = FALSE)
  
  # save standard curve plots
  #png(paste(wd, assayname, "_STD_CURVES.png", sep = ""))
  #plot(stdcurveplot)
  #dev.off()
  #ggsave(plot = stdcurveplot, path = figurespath, filename = "_STD_CURVES.png")
  
  
}
  
}

currentIteration <<- 1

# Apply the function to all data
QCoutput <- mapply(function(x, name) interpolateAndProcessData(x, name, headerrows, blankBeadCutoff, standardCurve, dilutionfactor, workingDirectory, dilutioncurvepath, sampledilutionpath, allData, allData.SamplingErrorsProcessed, allData.BeadCountProcessed, allData.CVProcessed, allData.BlankWellProcessed, allData.BlankBeadProcessed, currentIteration, cvCutoff, lowbeadcountcutoff, lowMFI), allData, names(allData), SIMPLIFY=FALSE)
```


